Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-08 talk/icooolps2009/paper.tex
try to fix the XXX

The results show that the tracing JIT speeds up the execution of this Python
function significantly, even outperforming CPython by a bit. The tracer needs to
trace through quite a bit of dispatching machinery of the Python interpreter to
achieve this, XXX.

>>>>

The results show that the tracing JIT speeds up the execution of this Python
function significantly, even outperforming CPython. \sout{by a bit. The tracer needs to
trace through quite a bit of dispatching machinery of the Python interpreter to
achieve this, XXX.}
\anto{
To achieve this, the tracer traces through the whole Python dispatching
machinery, automatically inlining only the relevant fast paths.
}
